\clearpage
\section*{International Food Policy Research Institute}

{\small
The International Food Policy Research Institute (IFPRI), a research center of CGIAR, provides
research-based policy solutions to sustainably reduce poverty and end hunger and malnutrition in low- and
middle-income countries. IFPRI was established in 1975 to identify and analyze alternative national and
international strategies and policies for meeting the food needs of the developing world, with particular
emphasis on low-income countries and on the poorer groups in those countries. Partnerships, communications, capacity strengthening, and data and knowledge management are essential components for
translating IFPRI’s research to action and impact. The Institute’s regional and country programs play a critical role in responding to demand for food policy research and in delivering holistic support to country-led development. IFPRI collaborates with partners around the world. 
\\
\href{https:\\www.ifpri.org}{www.ifpri.org}
}

\section*{CGIAR}

{\small
CGIAR is a global research partnership for a food-secure future, dedicated to transforming food, land, and
water systems in a climate crisis. CGIAR science aims to reduce poverty, enhance food and nutrition security, and improve natural resources and ecosystem services. As the world’s largest agricultural innovation
network, its research is carried out by 15 CGIAR Centers working around the world in close collaboration
with hundreds of partners, including national and regional research institutes, civil society organizations,
academia, development organizations, and the private sector.
\\
\href{https:\\www.cgiar.org}{www.cgiar.org}
}
\thispagestyle{empty}% Reset page style to 'empty"

\clearpage

\section*{Authors}
{\normalsize 

\textbf{Sherman Robinson} (\href{mailto:s.robinson@cgiar.org}{s.robinson@cgiar.org}) is a Research Fellow Emeritus at the Director General's Office of the International Food Policy Research Institute, Washington, D.C., USA. \\
\textbf{Shahnila Dunston} was a formerly a Senior Research Analyst at the Foresight And Policy Modeling unit of the International Food Policy Research Institute, Washington, D.C., USA. Shahnila is an Applied Economist - Climate Fellow at the Economic Research Service of the United States Department of Agriculture.
\\
\textbf{Abhijeet Mishra} (\href{mailto:a.mishra@cgiar.org}{a.mishra@cgiar.org}) is an Associate Research Fellow at the Foresight And Policy Modeling unit of the International Food Policy Research Institute, Washington, D.C., USA.
\\
\textbf{Timothy B. Sulser} (\href{mailto:t.sulser@cgiar.org}{t.sulser@cgiar.org}) is a Senior Scientist at the Foresight And Policy Modeling unit of the International Food Policy Research Institute, Washington, D.C., USA.
\\
\textbf{Daniel Mason-D’Croz} was formerly a Senior Research Analyst at the Environment and Production Technology Division the International Food Policy Research Institute, Washington, D.C., USA. Daniel is a Senior Research Associate at the Department of Global Development of the College of Agriculture and Life Sciences at Cornell University, Ithaca, New York, USA.
\\
\textbf{Richard Robertson} (\href{mailto:r.robertson@cgiar.org}{r.robertson@cgiar.org}) is a Research Fellow at the Foresight And Policy Modeling unit of the International Food Policy Research Institute, Washington, D.C., USA.
\\
\textbf{Nicola Cenacchi} (\href{mailto:n.cenacchi@cgiar.org}{n.cenacchi@cgiar.org}) is a Senior Research Analyst at the Foresight And Policy Modeling unit of the International Food Policy Research Institute, Washington, D.C., USA.
\\
\textbf{Tim Thomas} (\href{mailto:tim.thomas@cgiar.org}{tim.thomas@cgiar.org}) is a Senior Research Fellow at the Foresight And Policy Modeling unit of the International Food Policy Research Institute, Washington, D.C., USA.
\\
\textbf{Tingju Zhu} was formerly a Research fellow in the Environment and Production Technology Division of the International Food Policy Research Institute, Washington, D.C., USA.
\\
\textbf{Arthur Gueneau} was formerly a Research Analyst in the Development Strategy and Governance Division of the International Food Policy Research Institute, Washington, D.C., USA.
\\
\textbf{Gauthier Pitois} was formerly a Research Analyst in the Development Strategy and Governance Division of the International Food Policy Research Institute, Washington, D.C., USA.
\\
\textbf{Keith Wiebe} (\href{mailto:k.wiebe@cgiar.org}{k.wiebe@cgiar.org}) is a Senior Research Fellow at the Foresight And Policy Modeling unit of the International Food Policy Research Institute, Washington, D.C., USA and Lead of the CGIAR Research Initiative on Foresight.
\\
\textbf{Mark Rosegrant} (\href{mailto:m.rosegrant@cgiar.org}{m.rosegrant@cgiar.org}) is an IFPRI–Emeritus Fellow at the Director General's Office of the International Food Policy Research Institute, Washington, D.C., USA.
\\
}
\thispagestyle{empty}% Reset page style to 'empty"