\clearpage
\section*{Authors%\footnote{This version of IMPACT documentation is based on \cite{robinson2015international} and \cite{robinson2025international}. Sherwin Gabriel, Abhijeet Mishra and Timothy B. Sulser (re)incorporated aquatic foods in the model. Faaiqa Hartley, Nicola Cenacchi, Shahnila Dunston and Mark W. Rosegrant updated the base year of this model version and included the Intrinsic Productivity Growth Rate updates in the model based on \cite{hareau2025updating}. All other author names are in alphabetical order of family names.}
}

{\footnotesize 

TBD
\begin{multicols*}{2}

\begin{comment}

\textbf{Sherman Robinson} (\href{mailto:s.robinson@cgiar.org}{s.robinson@cgiar.org}) is a Research Fellow Emeritus at the Director General's Office of the International Food Policy Research Institute, Washington, D.C., USA. 

\vspace{0.07cm}
\textbf{Sherwin Gabriel} (\href{mailto:s.gabriel@cgiar.org}{s.gabriel@cgiar.org}) is a Scientist in the Foresight and Policy Modeling Unit of the International Food Policy Research Institute, Washington, D.C., USA.

\vspace{0.07cm}
\textbf{Abhijeet Mishra} (\href{mailto:a.mishra@cgiar.org}{a.mishra@cgiar.org}) is a Research Fellow at the Foresight and Policy Modeling unit of the International Food Policy Research Institute, Washington, D.C., USA.

\vspace{0.07cm}
\textbf{Faaiqa Hartley} (\href{mailto:f.hartley@cgiar.org}{f.hartley@cgiar.org}) is a Scientist in the Foresight and Policy Modeling Unit of the International Food Policy Research Institute, Washington, D.C., USA.

\vspace{0.07cm}
\textbf{Nicola Cenacchi} (\href{mailto:n.cenacchi@cgiar.org}{n.cenacchi@cgiar.org}) is a Senior Research Analyst at the Foresight and Policy Modeling unit of the International Food Policy Research Institute, Washington, D.C., USA.

\vspace{0.07cm}
\textbf{Timothy B. Sulser} (\href{mailto:t.sulser@cgiar.org}{t.sulser@cgiar.org}) is a Senior Scientist at the Foresight and Policy Modeling unit of the International Food Policy Research Institute, Washington, D.C., USA.

\vspace{0.07cm}
\textbf{Shahnila Dunston} was formerly a Senior Research Analyst at the Foresight and Policy Modeling unit of the International Food Policy Research Institute, Washington, D.C., USA.

\vspace{0.07cm}
\textbf{Daniel Mason-D’Croz} was formerly a Senior Research Analyst at the Environment and Production Technology Division the International Food Policy Research Institute, Washington, D.C., USA. Daniel is a Senior Research Associate at the Department of Global Development of the College of Agriculture and Life Sciences at Cornell University, Ithaca, New York, USA.

\vspace{0.07cm}
\textbf{Richard Robertson} (\href{mailto:r.robertson@cgiar.org}{r.robertson@cgiar.org}) is a Research Fellow at the Foresight and Policy Modeling unit of the International Food Policy Research Institute, Washington, D.C., USA.

\vspace{0.07cm}
\textbf{Tim Thomas} (\href{mailto:tim.thomas@cgiar.org}{tim.thomas@cgiar.org}) is a Senior Research Fellow at the Foresight and Policy Modeling unit of the International Food Policy Research Institute, Washington, D.C., USA.

\vspace{0.07cm}
\textbf{Tingju Zhu} was formerly a Research fellow in the Environment and Production Technology Division of the International Food Policy Research Institute, Washington, D.C., USA.

\vspace{0.07cm}
\textbf{Arthur Gueneau} was formerly a Research Analyst in the Development Strategy and Governance Division of the International Food Policy Research Institute, Washington, D.C., USA.

\vspace{0.07cm}
\textbf{Gauthier Pitois} was formerly a Research Analyst in the Development Strategy and Governance Division of the International Food Policy Research Institute, Washington, D.C., USA.

\vspace{0.07cm}
\textbf{Keith Wiebe} (\href{mailto:k.wiebe@cgiar.org}{k.wiebe@cgiar.org}) is a Senior Research Fellow at the Foresight and Policy Modeling unit of the International Food Policy Research Institute, Washington, D.C., USA and Lead of the CGIAR Research Initiative on Foresight.

\vspace{0.07cm}
\textbf{Mark W. Rosegrant} (\href{mailto:m.rosegrant@cgiar.org}{m.rosegrant@cgiar.org}) is an IFPRI–Emeritus Fellow at the Director General's Office of the International Food Policy Research Institute, Washington, D.C., USA.

\end{comment}

\end{multicols*}
}
\thispagestyle{empty}% Reset page style to 'empty"